Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
Cosmit and avoid footnote.
Let us not drown the reader into obvious details.

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$ -- called attributes or features -- and
some output variable $Y$. A sample is then defined as a tuple of values $(x_1,
..., x_p, y)$ of these variables and a dataset as a collection of such samples.
As such, matrices of numerical values\footnote{In the case of categorical
variables, numerical values can be obtained using various encoding schemes, such
as one-hot encoding.} constitute a natural representation used almost
unanimously within all areas of machine learning. In particular, each row in the
matrix then corresponds to a sample of the dataset and each column to one of the
variables of the problem.

>>>>

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$ -- called attributes or features -- and
some output variable $Y$. A sample is then defined as a tuple of values $([x_1,
..., x_p]^\mathrm{T}, y)$ of these variables and a dataset as a collection of
such samples.  As such, matrices of numerical values constitute a natural and
widely used representation in machine learning. In this view, each row in the
matrix then corresponds to a sample of the dataset and each column to one of the
variables of the problem.
